Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-21 article.tex
wording + commments

Figure \ref{fig:curves} shows the ROC curve  and precision-recall curve
for correlation, GTE and partial correlation on the \textit{normal-2}
dataset. The partial correlation outperforms other state-of-the-art methods
by at least factor of 2 in AUPRC reaching $0.347$ and an increased of $0.05$ in
AUROC. Two reasons might explain such differences: (i) among
those methods only the partial correlation makes the distinction between
direct and indirect connections, (ii) the simulated network from the
\citep{stetter2012model} generator or the neural network in general could be
reduced to a linear model after pre-processing. Those results is obviously
generalized over the other datasets see Appendix \textcolor{red}{REF}.

@@

As it can also be seen on Figure \ref{fig:curves}, the GENIE3 performance
increases with deeper trees in addition to be computationally feasible. The
reason is twofold. First, the deeper the tree, the larger is the conditioning.
As it was observed in the comparison between correlation and partial
correlation, it screens indirect links in the inferred network. Second, the
number of small trees need to be much higher than deep trees in order to
observe - and evaluate - all pairs.  However, as suggested by
\cite{louppe2014understanding}, limiting the maximal depth of trees may help
to improve the variable importance computing, i.e.
inferring the degree of association. Therefore a trade-off of the maximal depth
may give the best of both worlds.

>>>>

Figure \ref{fig:curves} shows the ROC curve  and precision-recall curve
for correlation, GTE and partial correlation on the \textit{normal-2}
dataset. The partial correlation outperforms other state-of-the-art methods
by at least factor of 2 in AUPRC reaching $0.347$ and an increased of $0.05$ in
AUROC. Two reasons might explain such differences: (i) among
those methods only the partial correlation makes the distinction between
direct and indirect connections, (ii) the simulated network from the
\citep{stetter2012model} generator or neural networks in general could be
reduced to a linear model after pre-processing. Those results is obviously
generalized over the other datasets see Appendix \textcolor{red}{REF}.

@@

As observed on Figure \ref{fig:curves}, the GENIE3 performance
increases with deeper trees while being still computationally feasible. The
reason is twofold. First, the deeper the tree, the larger is the conditioning.
\textcolor{red}{AJ: conditioning?}
As it was observed in the comparison between correlation and partial
correlation, it screens indirect links in the inferred network.
\textcolor{red}{AJ: I don't understand the link with GENIE3}
Second, the
number of small trees need to be much higher than deep trees in order to
observe - and evaluate - all pairs.  However, as suggested by
\cite{louppe2014understanding}, limiting the maximal depth of trees may help
to improve the variable importance computing, i.e.
inferring the degree of association. \textcolor{red}{AJ: there is no explanation
of why it would be better apart for computational reason.} Therefore a trade-off
 of the maximal depth may give the best of both worlds. \textcolor{red}{AJ:
 Which tradeoff? Which worlds?}
